#### [**Means Tested Solar Subsidies**](papers/colas-reynier-income-solar.pdf)
with [Mark Colas](https://sites.google.com/site/markyaucolas/home)
*Revisions resubmitted, Journal of Political Economy Microeconomics.*

We study income-contingent subsidies for residential solar panels. We develop sufficient statistics for evaluating the cost-effectiveness of means-tested subsidies and estimate them using remotely sensed data on solar panel installations across the US and a border-discontinuity design. Our estimates show that the responsiveness of installation rates to subsidies is decreasing in income, with the largest differences in the first and fourth income quartiles. A structural model reveals that switching to production-maximizing income-contingent solar subsidies increases the share of public funds received by low-income households while increasing national solar production. Means-tested subsidies are justified on equity and efficiency grounds.

[Current draft](papers/colas-reynier-income-solar.pdf), [CESifo Working Paper No. 11378](https://www.cesifo.org/node/83083).

```{r}
#| label: pvincome
#| echo: false
#| layout-ncol: 1
include_image("images/nonadditionality-fixed-subsidy.jpeg")
```

<br>

#### **[The Distributional Impacts of Climate Change across U.S. Local Labor Markets](papers/reynier-morehouse-climate-migration.pdf)**
with [John Morehouse](https://www.johnmmorehouse.com/)

Climate change has affected households around the globe, but its impacts are not homogenous across space. We first show that disadvantaged demographic groups are disproportionately exposed to climate change in the US and are less responsive in their adaptive behavior. Motivated by these findings, we develop and estimate a spatial equilibrium model of US local labor markets, allowing households to adapt to climate change by choosing where to live and, conditional on that choice, energy and housing consumption. Our results show that climate change to date has caused welfare losses 20\% larger for black households relative to white households and twice as large for the lowest income decile relative to the highest income decile. We estimate that these gaps will continue to grow under projections of the future climate. Both the population's ex-ante distribution and differential mobility contribute to the observed disparities. We then evaluate a \$3 billion place-based policy from the Inflation Reduction Act, quantifying the tradeoff between subsidzing places with high climate damages and the resulting in-migration to climate-exposed areas.

[Current Draft](papers/reynier-morehouse-climate-migration.pdf)

```{r}
#| label: jmp
#| echo: false
#| layout-ncol: 2
include_image("images/prism-grid-hot-days-1990-2019.jpeg")
include_image("images/inc-q10-cv-perc-5y.jpeg")
```

<br>
